### 2021-02-13 background.tex
fisrt revision introduction,backgroud,set. result first version

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network or other device data. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application. It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.

The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security. The technique comprises of two steps. First, rules are mined and will compose the sandbox \kn{I thought sandbox was an environment, now it is comprised of rules?}, through test generator tools. These tools explore program behavior and monitor access to sensitive APIs. The second stage ensures that resources not accessed, or accessed differently, at first stage, are denied access. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

@@

Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In this~\kn{This meaning our paper or the droidbot paper, then use "their work"} paper, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} as a proof of concept example of using DroidBot in malware analysis~\kn{What is being compared with what. Is droidbot compared with monkey. If yes, then what is the proof  of concept example of using Droidbot? Something we have built. Or is the comparison between Droidbot and Monkey as an example of using droidbot?}. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot. This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, and after combining all test generator tools, it was possible to detect 80\% of malicious behavior. However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation. The way it was explained to me is not evident here. Especially the "interference of static analysis" requires expansion something in the lines of "The papers did not explore what happens when an existing static analysis in the background is removed, and how much of the analysis results actually come from existing static analysis"}.

>>>>

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network or other device data. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application.

%It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.

The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security. The sandboxing technique comprises of two steps. First, rules are miner and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools. These tools explore program behavior and monitor access to sensitive APIs. The second stage ensures that resources not accessed, or accessed differently, at first stage, are denied access. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

@@

Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} at a malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey. From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

%~\kn{What is being compared with what. Is droidbot compared with monkey. If yes, then what is the proof  of concept example of using Droidbot? Something we have built. Or is the comparison between Droidbot and Monkey as an example of using droidbot?}.

L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot. This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$). However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation. The way it was explained to me is not evident here. Especially the "interference of static analysis" requires expansion something in the lines of "The papers did not explore what happens when an existing static analysis in the background is removed, and how much of the analysis results actually come from existing static analysis"}.

### 2021-02-13 introduction.tex
fisrt revision introduction,backgroud,set. result first version

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes. Given an app A, a sandbox S identifies sensitive resources access by app A, during dynamic analysis, and then block calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.

@@

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a performance kn{performance or accuracy/ precision?} of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 describes all the apps malware used in our experiment, presenting their characterization. Section 4 introduces the study setting of our research. Section 5 presented some results, highlighting some motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

>>>>

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes. In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic analysis, and then block future calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.

@@

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 describes all malware apps used in our experiment, presenting their characterization. Section 4 introduces the study setting of our research and Section 5 complements presenting some results, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-02-13 results.tex
fisrt revision introduction,backgroud,set. result first version

In this section, we present the finding of our study. We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study.

@@

Our first study performed a non-exact replication of Bao et al work. Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox. We could use all 102 pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.

@@

\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among 96 pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed 102 pairs, the percent is close. At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among 102 (66,66\%). However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect 54 malware. Despite this reduction, it had the largest number of malicious apps detected in this new situation.

@@

Considering the static analysis provided by Droidfax, and Flowdroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%). We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm. Table \ref{tab:recursos} compile the results of this comparison.

@@

\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
\end{tabular} 
\caption{Comparison between Droidfax and Flowdroid algorithms}
\label{tab:recursos}
\end{table}

Furthermore, we can highlight that among 19 pair apps that at our first study, were not detected by the sandboxes constructed by test generation tool and static analysis Droidfax miner, 4 could be detected by Flowdroid; P35, P38, P56, and P94, therefore exposing, better accuracy of the static analysis algorithms. Among these 4 pairs detected, 2 were trojans, 1 was the exploit, the only no detected, and 1 was adware.

>>>>

In this section, we present the finding of our study. We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study (Section V-C).

@@

Our first study performed a non-exact replication of Bao et al work. Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox. We could use all $102$ pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.

@@

\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among $96$ pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed $102$ pairs, the percent is close. At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among $102$ (66,66\%). However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect $54$ malware. Despite this reduction, it had the largest number of malicious apps detected in this new situation.

@@

Considering the static analysis provided by Droidfax, and Flowdroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%). We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm. Table \ref{tab:comparison} compile the results of this comparison.

@@

\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
\end{tabular} 
\caption{Comparison between Droidfax and Flowdroid algorithms}
\label{tab:comparison}
\end{table}

Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis Droidfax miner, 4 were detected by Flowdroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms. Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.

\subsection{Result Summary}

First we find that static analysis summaries had impact in the Bao et al. study. It was responsible for improving the results of the tools by 47.78\% than its executions alone, answering our first research question (RQ1). Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2). We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was Droidbot, proving be the tool with better effective performance, in terms of the number of detected malware. Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms. Our experiment highlight that 69.79\%-81.25\% of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that 
sandboxes can be further boosted when coupled with new static analysis techniques. We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, 81.25\% with Monkey, a better performance than all five tools explored at Bao et al., even when they combined all the tools together at theirs work 75.49\%. Table \ref{tab:tanted} display the increase of all tools explored at our research.

\begin{table}[ht]
\centering
\begin{tabular}{lccc}\toprule
 Test Generation & FlowDroid & Total & \%\\
 Tool & Increase  &  & \\ \midrule
 Monkey & 7 & 78 & 81.25\\
 Droidmate & 10 &  74 & 77.08 \\
 Humanoid & 20 & 69 & 71.87  \\
 Joke & 25 & 67 & 69.79 \\
 Droidbot & 9 & 77 & 80.20  \\\midrule

\end{tabular} 
\caption{Malwares detected in 96 pair (B/M) increased by Tainted analysis Algorithms}
\label{tab:tanted}
\end{table}

### 2021-02-13 setup.tex
fisrt revision introduction,backgroud,set. result first version

In this section, we present the settings of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} and thus build
a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve
the performance of mining sandboxes, in the task of identifying malicious behavior.

@@

\begin{enumerate}[(RQ1)]
 \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?

@@

Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation of the performance of test generation tools for mining sandboxes,
as reported by Bao et all.~\cite{DBLP:conf/wcre/BaoLL18}, which might introduce a possible threat to their conclusions. Answering the third research question
allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
dynamic analysis through the use of static analysis algorithms.

We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work.
For that purpose, we initially selected four test generation tools: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, Monkey~\cite{Monkey}, and Humanoid~\cite{DBLP:conf/kbse/LiY0C19}. The first three have
been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior in the original work. We also selected Monkey because it is the most popular test
generation tool for Android, coming up with the Android SDK installation. Finally, we selected Humanoid  because it is a recent test generation tool,
which generates human-like test inputs using deep learning techniques and promises to achieve higher code coverage
than state-of-the-art test generation tool. 
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

In the second study we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to execute
tainted analysis algorithms in Android apps, in order to identify pairs of \emph{sources and sinks}. In this case,
our goal is to investigate the performance on detecting malicious
behavior using static taint analysis of Android apps. We use two metrics in this second study: the number
of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M) and the
execution time of the analysis for each app.
For both studies, we employed the same dataset 98 pairs of Android apps (B/M),
shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail the procedures of each study in what follows.

>>>>

%\kn{This paragraph requires a motivation. The details of Boa's study must be described upfront. Something like "Boa et al.'s study performs ..... Since their study also involved a static analysis component whose impact was not measured, we perform a non-exact replication to understand the impact static analysis may have had in the results...}

Bao et al.'s ~\cite{DBLP:conf/wcre/BaoLL18} study explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis. Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results. Thus, this section present the settings of our study, whose goal is to perform this non-exact replication, and thus build a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.

@@

\begin{enumerate}[(RQ1)]

 \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?

@@

%\kn{Droidfax comes out of nowhere. We should introduce this or if already introduced earlier, remind the readers of where it stands with the Bao study in the first line of this section when describing boas study}

Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
as reported by Bao et al., which might introduce a possible threat to their conclusions. Answering the third research question
allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
dynamic analysis through the use of static analysis algorithms.

We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work.
For that purpose, we initially selected four test generation tools: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, Monkey~\cite{Monkey}, and Humanoid~\cite{DBLP:conf/kbse/LiY0C19}. The first three have
been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Monkey was developed for stress testing and can not perform text input. Therefore, we also selected Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

In the second study we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to execute
tainted analysis algorithms in Android apps, in order to identify pairs of \emph{sources and sinks}. In this case,
our goal is to investigate the performance on detecting malicious
behavior using static taint analysis of Android apps. We use two metrics in this second study: the number
of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M) and the
execution time of the analysis for each app.
For both studies, we employed the same dataset $96$ pairs of Android apps (B/M),
shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail the procedures of each study in what follows.
